Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-05-13 doc/report/msc-report.tex
report style; non-hardcoded paths in Makefile
added TODOs fixed most of Dave's comments

\documentclass[a4paper,10pt]{book}

\author{Per Andersson, Fredrik M{\"o}llerstrand}

\title{Zohmg---a large scale data store for aggregated time-series-based
data. [DRAFT]}

% chapterquote
\newcommand{\chapterquote}[2] {
\begin{quote}
\textit{"{#1}"}

--- {#2}
\end{quote}

\vspace{24pt}
}

\begin{document}

\maketitle

\noindent \Large{\textbf{Abstract}}

\noindent

@@

\tableofcontents

\vfill

@@

Any organization will eventually wish to analyze various characteristics of
its service and operations. These services can be anything from web sites to
theme parks. The analysis might include characteristics such as the number of
visitors per day, or the average time a theme park guest spends queueing for a
particular ride.

@@

After having collected these base facts, one can draw conclusions about what
countries generate the most traffic to the site, and which web browser is most
popular in a certain country, and so on.

Typically, the size of a data set is in the range of several gigabytes of data
per day. Some data sets are many times larger.

@@

@@

@@

% TODO: Why do we do these avgränsningar.

@@

@@

HDW is system which goal is to create a high performance large scale data
warehouse based on MapReduce and Bigtable. \cite{hdw}

@@

@@

@@

TODO: Time series is one of the most important measures in log analyzing, it
is also very natural when the data is time-stamped. \cite{discoveringweb}

@@

@@

The classic trade-off between time and space applies to whether or not
pre-compute an aggregate. Pre-computing to many aggregates might render an
unfeasible amount of data to store, while pre-computing to few aggregates
renders longer access times for aggregates which are not pre-computed. This
problem is further discussed in the thesis, but left to the user of the
Zohmg system to solve.

@@

TODO: Why do we chose HBase in favour of other techniques (i.e. SQL)?

@@

\textbf{TODO: -- elaborate on reasons to why starsql does not scale--}

@@

A data warehouse is a repository of an organization's electronically stored
data. Data warehouses are designed to facilitate reporting and analysis.
\cite{wikipedia}

@@

>>>>

% chapterquote command.
\newcommand{\chapterquote}[2] {
\begin{quote}
\textit{"{#1}"}

--- {#2}
\end{quote}
\vspace{24pt}
}

\documentclass[a4paper]{report}

\author{Per Andersson, Fredrik M{\"o}llerstrand}
\title{Zohmg---a large scale data store for aggregated time-series-based
data. [DRAFT]}

\begin{document}
\maketitle

\noindent {\Large \textbf{Abstract}}
\vspace{12pt}
\noindent

% TODO: use less buzzwords; focus on the problem.

@@

\tableofcontents
\vfill
\pagebreak

@@

% TODO: introduce time-series, data warehousing, mapreduce, bigtable
% TODO: why is time important? (we query for time, etc.)

Any organization will eventually want to analyze various characteristics of
its service and operations. The services can be anything from web sites to
theme park; the analysis might include characteristics such as the number of
visitors per day, or the average time a theme park guest spends queueing for a
particular ride.

@@

When the records in the data set have been analyzed, one can draw conclusions
about what countries generate the most traffic to the site, which web browser
is most popular in a certain country, etc.

The size of the data sets at last.fm is in the range of several gigabytes per
day. Some data sets are many times larger. It is our belief that this is
typical.

@@

% TODO: write about how mapreduce already solves the problem of parallel
% computation, and how gfs solves the problem of distributed storage.

@@

% TODO: define aggregates!

@@

% TODO: argue why we do these avgränsningar.

@@

% TODO: this section.

@@

HDW is a system whose goal is to create a high performance large scale data
warehouse based on MapReduce and Bigtable. \cite{hdw}

@@

% TODO: make correct.
The following overview is entirely incorrect:

@@

% TODO: example.

@@

% TODO: this section.

Time series is one of the most important measures in log analyzing, it
is also very natural when the data is time-stamped. \cite{discoveringweb}

@@

% TODO: be clear about how aggregates are *derived* from one or several vars.
% TODO: example.

@@

The classic trade-off between time and space applies to whether or not to
pre-compute an aggregate. Pre-computing too many aggregates might result in an
unfeasible amount of data, while pre-computing too few aggregates results in
longer access times for those aggregates that were not pre-computed.

@@

% TODO: Why do we chose HBase in favour of other techniques (i.e. SQL)?

@@

% TODO: elaborate on reasons to why starsql does not scale

@@

\section{Stop making speeches}
A data warehouse is a repository of an organization's electronically stored
data. Data warehouses are designed to facilitate reporting and analysis.
\cite{wikipedia}

@@

\section{It's not like the movies}
